---
title: "VariantVisualizer"
author: "Wisse Schuuring"
date: "2024-08-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
This R markdown document is part of a larger snakemake pipeline project called NewDataProcessProject,
and thus is to be used within that pipeline only.

https://github.com/WisseSchuuring/NewDataProcessProject


## Input File

The snakemake pipeline creates a csv report using pangolin. This csv report documents the ambiguity score,
which is a function of the quantity of missing data in a sequence. It represents the proportion of relevant
sites in a sequence which were assigned to the reference values. A score of 1 indicates that no sites were
imputed, while a score of 0 indicates that more sites were imputed than were not imputed. This score only
includes sites which are used by the decision tree to classify a sequence.

```{r test dataframe}
df <- data.frame(sequence_name = c("Africa_variant_R1","Africa_variant_R2", "UK_variant_R1", "UK_variant_R2"), lineage = c("B","B","A","A.1"))
print(df)

```


```{r csv reader}
# Read in the csv file from the pangolin program
read_pangolin <- function(file_path){
  pangolin_output <- read.csv(file=file_path, sep=",", header=T)
}

df <- read_pangolin(file_path = snakemake@input[[1]])
```

## Plots

```{r plot, echo=FALSE}
# create the barplot
create_barplot <- function(data, names){
   barplot(height=data,
           ylab = "lineage",
           xlab = "lineage amount",
           main = "Amount of assigned sequences by lineage",
           col="lightgreen",
           horiz = T)
}


# Export the barplot as a png
png(snakemake@output[[1]])
create_barplot(table(df$lineage))

    
```

